Figures

### 2019-11-01 figures/07_model-selection.Rmd
indexing typo fix

```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
# autoselect best tn model
re_names <- unlist(lapply(re_brms, function(x) 
  get_re_text(as.character(x$formula)[[1]])))[seq((length(re_brms)/2) + 1,
                                                  length(re_brms))]
best_tn <- loo_compare(
  lapply(seq((length(re_brms)/2) + 1, length(re_brms)), 
         function(x) re_brms[[x]]$loo))
best_tn <- which(re_names == row.names(best_tn)[1])

>>>>

```{r pre_tn_fe, out.width="3.45in", out.height="4in"}
# autoselect best tn model
re_names <- unlist(lapply(re_brms, function(x) 
  get_re_text(as.character(x$formula)[[1]])))[seq((length(re_brms)/2) + 1,
                                                  length(re_brms))]
best_tn <- loo_compare(
  lapply(seq((length(re_brms)/2) + 1, length(re_brms)), 
         function(x) re_brms[[x]]$loo))
best_tn <- which(re_names == row.names(best_tn)[1]) + (length(re_brms)/2)
